Data Management for LSST Special Programs

### 2023-10-19 sec_proc.tex
cite sheppard et al.

\item \textbf{Twilight images --}
For Special Programs which obtain images with very bright sky backgrounds
(twilight images), it is currently unclear whether they can be processed
with the LSST Science Pipelines; User-Generated Processing might be needed.

@@

Since Solar System Processing takes {\tt DiaSource}s as input, any 
Special Programs images that are processed by the Prompt pipeline
could be incorporated into Solar System Processing as well.

>>>>

\item \textbf{Twilight images --}
For Special Programs which obtain images with very bright sky backgrounds
(twilight images), it is currently unclear whether they can be processed
with the LSST Science Pipelines; 
User-Generated Processing might be needed (e.g., \citealt{2022AJ....164..168S}).

@@

Since Solar System Processing takes {\tt DiaSource}s as input, any 
Special Programs images that are processed by the Prompt pipeline
could be incorporated into Solar System Processing.
